---
title: "p8105_hw5_jl5295"
author: "Jana Lee"
date: "11/5/2019"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(p8105.datasets)
library(ggplot2)
library (knitr)
library(viridis)
library(broom)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%")
```

## Problem 1
```{r code chunk from problem}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

```{r writing functions}
fill_missing_values = function(x) {
  if (is.numeric(x)) {
  replace(x, is.na(x), mean(x, na.rm = TRUE)) 
}
  
  else if (!is.numeric(x)) {
    replace(x, is.na(x), "virginica")
  }
}

iris_without_missing = map_df(iris_with_missing, ~fill_missing_values(.x))
```
**Comment:** A new dataframe `iris_without_missing` was generated to test if the function works. `iris_without_missing` has correctly computed the mean value for all numeric missing values and has applied to word "virginica" to all missing character values.


## Problem 2
```{r iteration of csv files for longitudinal study}
csv_data = list.files("./data", pattern = "*.csv", full.names = TRUE) %>% 
  set_names(nm = basename(.)) %>% 
  map_df(read_csv, col_names = TRUE, col_types = cols(), .id = "filename") %>%
  mutate(
    arm = str_sub(filename, 1,3),
    id = str_sub(filename, 5,6)) %>% 
  select(arm, id, week_1:week_8) %>% 
  mutate(
    arm = replace(arm, arm == "con", "control"),
    arm = replace(arm, arm == "exp", "experiment")) %>%
   unite(participant_data, c(arm, id), remove = TRUE) %>% 
  pivot_longer(-participant_data,
    names_to = "week_number",
    values_to = "count") %>%  
  ggplot(aes(
    x = week_number, 
    y = count, 
    group = participant_data, 
    color = participant_data)) +
  geom_line() +
  labs(
    x = "Week Number",
    y = "Count of Treatment Response",
    title = "Count of Treatment Response for Experimental and Control Arms over 8 weeks")

csv_data + labs(color = "Participant Arm and Week")
```
**Comment:** Assuming that higher positive values signify better response, participants in the experimental arm are more likely to have higher responses to treatment, judging from the blue to purple coloring of the lines. Similarly, controls, indicated by the red to green coloring, have lower responses and have a higher frequency of having negative response values (i.e. control patient, week 5). More context to this dataset would allow us to glean further insight about the responses to this longitudinal study.


## Problem 3
```{r setting up design elements for simulation, echo = TRUE, message = FALSE, warning = FALSE}
set.seed(5)

simple_linear_regression = function(n = 30, beta0 = 2, beta1 = 0, variance = 50) {
  
  prob_3 = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, sqrt(50))
  )
  
  linear_fit = lm(y ~ x, data = prob_3) %>% 
  tidy()
  
}

regression_results = 
  rerun(10000, simple_linear_regression(beta1 = 0)) %>% 
  bind_rows() %>% 
  filter(term == "x") %>% 
  select(estimate, p.value)

``` 


```{r repeat for beta1-6, echo = TRUE, message = FALSE, warning = FALSE}
prob_3_final = tibble(beta1_new = c(0, 1, 2, 3, 4, 5, 6)) %>% 
  mutate(
    output_lists = map(.x = beta1_new, ~rerun(10000, simple_linear_regression(beta1 = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>%
  filter(term == "x") %>%
  select(-output_lists) %>% 
  unnest(estimate_dfs)

```

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of β2 on the x axis. Describe the association between effect size and power.

### Plot of Power and Effect Size
```{r plot 1}
plot_1 = prob_3_final %>%
  mutate(reject = ifelse(p_value < 0.05, "Significant", "Not Significant")) %>%
  group_by(beta1_new, reject) %>%
  summarize(rejection_count = n()) %>%
  filter(reject == "Significant") %>%
  mutate(rejection_rate = rejection_count/100) %>%
ggplot(aes(x = beta1_new, y = rejection_rate)) + 
    geom_point() +
    geom_line() + 
    labs(
    title = "Association Between Power and Effect Size",
    x = "Effect Size",
    y = "Power")

plot_1
```
**Comment:** As effect size increases, power also increases. This levels off around a power of approximately 80.


### Plot 2
```{r}
plot_2 = regression_results %>%
  mutate(reject = ifelse(p_value < 0.05, "Significant", "Not Significant")) %>%
  group_by(beta1_new) %>%
  summarize(mean_b1= mean(beta1_hat)) %>%
ggplot(aes(x = beta1_new, y =mean_b1)) + 
    geom_point() +
    geom_line() + 
    labs(
    title = "Relationship Between the Beta 1 True Value and the Mean estimate of Beta 1",
    x = "True Value of Beta 1",
    y = "Mean estimate of Beta 1")

plot_2
```

