---
title: "p8105_hw5_jl5295"
author: "Jana Lee"
date: "11/5/2019"
output: html_document
---

## Problem 1
The code chunk below loads the iris dataset from the tidyverse package and introduces some missing values in each column. The purpose of this problem is to fill in those missing values.
There are two cases to address:

For numeric variables, you should fill in missing values with the mean of non-missing values
For character variables, you should fill in missing values with "virginica"
Write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector. Apply this function to the columns of iris_with_missing using a map statement.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(p8105.datasets)
library(ggplot2)
library (knitr)
library(viridis)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```



## Problem 2
This zip file contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

Start with a dataframe containing all file names; 
-the list.files function will help
- Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
-Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups
```{r}
csv_data = list.files("./data", pattern = "*.csv", full.names = TRUE) %>% 
  set_names(nm = basename(.)) %>% 
  map_df(read_csv, col_names = TRUE, col_types = cols(), .id = "filename") %>% 
  mutate(
    arm = str_sub(filename, 1,3),
    id = str_sub(filename, 5,6)) %>% 
  select(arm, id, week_1:week_8) %>% 
  mutate(
    arm = replace(arm, arm == "con", "control"),
    arm = replace(arm, arm == "exp", "experiment")) %>% 
  mutate(participant = str_c(week_1::week_8, collapse = " ")) %>% 
  pivot_longer(
    names_to = "week_number",
    values_to = "count"
    )

df %>% mutate(x=str_c(n,"-",s,".",b))

view(csv_data)
```


## Problem 3
When designing an experiment or analysis, a common question is whether it is likely that a true effect will be detected – put differently, whether a false null hypothesis will be rejected. The probability that a false null hypothesis is rejected is referred to as power, and it depends on several factors, including: the sample size; the effect size; and the error variance. In this problem, you will conduct a simulation to explore power in a simple linear regression.

First set the following design elements:

Fix n=30
Fix xi1 as draws from a standard Normal distribution
Fix β0=2
Fix σ2=50
Set β1=0. Generate 10000 datasets from the model
yi=β0+β1xi1+ϵi
with ϵi∼N[0,σ2]. For each dataset, save β̂ 1 and the p-value arising from a test of H:β1=0 using α=0.05. Hint: to obtain the estimate and p-value, use broom::tidy to clean the output of lm.

Repeat the above for β1={1,2,3,4,5,6}, and complete the following:

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of β2 on the x axis. Describe the association between effect size and power.
Make a plot showing the average estimate of β̂ 1 on the y axis and the true value of β1 on the x axis. Make a second plot (or overlay on the first) the average estimate of β̂ 1 only in samples for which the null was rejected on the y axis and the true value of β1 on the x axis. Is the sample average of β̂ 1 across tests for which the null is rejected approximately equal to the true value of β1? Why or why not?
```{r}

```

